%------------------------------------------------------------------------------
% Resume in LaTeX
% Candidate : Ismael Belem
% Based off of: https://github.com/fizixmastr (Charles Rambo template)
% License : MIT
%------------------------------------------------------------------------------

\documentclass[A4]{article}
%\documentclass[letterpaper,11pt]{article} %For use in US
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
\input{glyphtounicode}

%-----FONT OPTIONS-------------------------------------------------------------
% serif
\usepackage{palatino}
% \usepackage{times}
% \usepackage{charter}

% sans-serif
% \usepackage{helvet}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

%-----PAGE SETUP---------------------------------------------------------------

\addtolength{\oddsidemargin}{-0.5 cm}
\addtolength{\evensidemargin}{-0.5 cm}
\addtolength{\textwidth}{1 cm}
\addtolength{\topmargin}{-0.5 cm}
\addtolength{\textheight}{1 cm}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0cm}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that .pdf is machine readable / ATS parsable
\pdfgentounicode=1

%-----CUSTOM COMMANDS----------------------------------------------------------
\newcommand{\CVItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\CVSubheading}[4]{
  \vspace{-4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\CVSubItem}[1]{\CVItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\CVSubHeadingListStart}{\begin{itemize}[leftmargin=0.5cm, label={}]}
\newcommand{\CVSubHeadingListEnd}{\end{itemize}}
\newcommand{\CVItemListStart}{\begin{itemize}}
\newcommand{\CVItemListEnd}{\end{itemize}\vspace{-5pt}}

%------------------------------------------------------------------------------
% RESUME STARTS HERE
%------------------------------------------------------------------------------
\begin{document}

%-----HEADER-------------------------------------------------------------------
\begin{flushleft}
    \textbf{\Large \scshape{Ismael Belem}} \\ \vspace{5pt}
    \small{North Bergen, NJ} \\
    \small{929-326-8527} \\
    \href{mailto:belem2010@hotmail.fr}{\underline{belem2010@hotmail.fr}} \\
    \href{https://www.ismaelbelem.com}{\underline{https://www.ismaelbelem.com}} \\
    \href{https://www.linkedin.com/in/ismael-belem-95bb08173/}{\underline{linkedin.com/in/ismael-belem-95bb08173}} \\
    \href{https://github.com/Ibelem1}{\underline{github.com/Ibelem1}} \\
\end{flushleft}

%-----PROFESSIONAL SUMMARY----------------------------------------------------
\section{Professional Summary}
\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \small{Results-driven Cybersecurity Analyst with 4+ years in blue team operations, incident response, and digital forensics. Experienced in leveraging SIEM (Microsoft Sentinel, Wazuh, Splunk) and EDR (CrowdStrike Falcon, Microsoft Defender) to protect 400+ endpoints across public cloud (Azure, AWS, GCP), hybrid, and on-prem environments. Proven track record in reducing false-positive alerts by 25\%, leading SOC teams, and conducting comprehensive security gap assessments. Skilled in developing SOPs, performing threat hunting, analyzing adversary TTPs and IOCs, and delivering executive-level security briefings to technical and non-technical stakeholders.}
\end{itemize}

%-----EXPERIENCE---------------------------------------------------------------
\section{Professional Experience}
  \CVSubHeadingListStart

    \CVSubheading
      {Cybersecurity Analyst II $|$ Dataprise (MSSP)}{Sep 2023 -- Present}
      {North Bergen, NJ}{}
      \CVItemListStart
        \CVItem{Designed and deployed enterprise detection and telemetry dashboards in CrowdStrike LogScale and Microsoft Sentinel (KQL), improving SOC visibility across managed environments.}
        \CVItem{Implemented automated host containment workflows (Attack Disruption) using CrowdStrike Fusion SOAR to isolate compromised systems based on vetted detection alerts.}
        \CVItem{Served as the highest technical escalation point for SOC investigations, supporting incident response engagements involving advanced threat actors and enterprise breaches.}
        \CVItem{Conducted proactive threat hunting and adversary infrastructure analysis using telemetry, OSINT sources, adversary TTPs, and emerging intelligence feeds.}
        \CVItem{Monitored and investigated security alerts across CrowdStrike Falcon and Microsoft Sentinel, analyzing host telemetry and log data to identify IOCs, IOAs, and potential compromise.}
        \CVItem{Conducted incident investigations including malware detections, account compromise, and unauthorized activity across managed environments.}
        \CVItem{Managed over 400 endpoints using CrowdStrike: enforced EDR policies, coordinated sensor deployments, and developed detection workflows and automated playbooks using PowerShell and Python.}
        \CVItem{Security awareness training (KnowBe4, PII-Protect ``Breach Secure Now''): oversaw 200 accounts, created automated training programs, phishing simulations, and monthly newsletters.}
        \CVItem{Appointed by Cyber Department President to lead vendor evaluation project assessing cybersecurity awareness tools -- measuring efficiency, scalability, and AI capabilities.}
        \CVItem{Led creation of incident response SOPs and playbooks; trained Tier 1 SOC analysts and delivered monthly client briefings including vulnerability and remediation reports.}
        \CVItem{Provided ongoing intelligence briefings on emerging threats, adversary TTPs, cybercrime trends, and new IOCs to SOC analysts and client stakeholders.}
      \CVItemListEnd

    \CVSubheading
      {Cybersecurity Engineer $|$ Cohere Cyber Secure (MSSP)}{Sep 2022 -- Sep 2023}
      {Manhattan, NY}{}
      \CVItemListStart
        \CVItem{Provided overall security posture assessments in After-Action Reports covering penetration testing scope, risk management, mitigation strategies, and lessons learned.}
        \CVItem{Triaged security incidents including ransomware, following the Incident Response Framework and performing host- and network-based forensics to determine root cause and preserve evidence.}
        \CVItem{Configured policies in CrowdStrike Falcon to harden environments and prevent attacker lateral movement.}
        \CVItem{Monitored, created detection rules, and onboarded clients to SIEM (Wazuh), developing custom rules and parsers using regex and threshold tuning to improve alert fidelity.}
        \CVItem{Developed Incident Response, ransomware, phishing, and Wazuh deployment SOPs and playbooks to standardize response and onboarding procedures.}
        \CVItem{Conducted quarterly Vulnerability Assessments using Nessus and CrowdStrike; applied CVSS scoring, communicated findings to clients, and coordinated remediation planning.}
        \CVItem{Monitored and analyzed Linux operating systems for security threats and vulnerabilities, implementing timely remediation.}
      \CVItemListEnd

    \CVSubheading
      {Operations Manager $|$ Bocaphe}{Jan 2020 -- Sep 2022}
      {Manhattan, NY}{}
      \CVItemListStart
        \CVItem{Conducted recruitment, training, and scheduling of new employees.}
        \CVItem{Provided support for all internal POS systems and utilized AnyDesk/TeamViewer for tablet-based computer troubleshooting.}
        \CVItem{Facilitated software setup for new technological products and internal systems.}
      \CVItemListEnd

    \CVSubheading
      {Freelance IT Technician $|$ Self-Employed}{Jan 2013 -- Sep 2021}
      {Ouagadougou, Burkina Faso \& Manhattan, NY}{}
      \CVItemListStart
        \CVItem{Provided maintenance and hardware upgrades for PCs and laptops.}
        \CVItem{Installed and configured operating systems, VMware, Wireshark, antivirus, Office 365, Azure, and Linux.}
        \CVItem{Delivered IT support assistance to third-party clients.}
      \CVItemListEnd

  \CVSubHeadingListEnd

%-----EDUCATION----------------------------------------------------------------
\section{Education}
  \CVSubHeadingListStart

    \CVSubheading
      {{Master of Science $|$ \emph{\small{Digital Forensics and Cybersecurity}}}}{May 2022}
      {John Jay College of Criminal Justice (CUNY)}{New York, NY}

    \CVSubheading
      {{Advanced Certificate $|$ \emph{\small{Applied Digital Forensics (A.C. P.B.)}}}}{May 2022}
      {John Jay College of Criminal Justice (CUNY)}{New York, NY}

    \CVSubheading
      {{Bachelor of Science $|$ \emph{\small{Computer Science and Information Security}}}}{Dec 2020}
      {John Jay College of Criminal Justice (CUNY)}{New York, NY}

    \CVSubheading
      {{Associate of Science $|$ \emph{\small{Computer Network Technology}}}}{May 2019}
      {Borough of Manhattan Community College (CUNY)}{New York, NY}

  \CVSubHeadingListEnd

%-----CERTIFICATIONS-----------------------------------------------------------
\section{Certifications}
\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \textbf{CrowdStrike Certified Falcon Administrator} -- CCFA-200
    \item \textbf{Microsoft Certified: Security Operations Analyst Associate} -- SC-200
    \item \textbf{Microsoft Certified: Azure Administrator Associate} -- AZ-104
    \item \textbf{Microsoft Certified: Security, Compliance, and Identity Fundamentals} -- SC-900
    \item \textbf{CompTIA Security+} -- SY0-601
\end{itemize}

%-----SKILLS-------------------------------------------------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.5cm, label={}]
    \item \textbf{SIEM \& EDR}: Microsoft Sentinel, Splunk, Wazuh, CrowdStrike Falcon, Microsoft Defender for Endpoint, CrowdStrike LogScale, KQL
    \item \textbf{Threat Hunting \& IR}: Threat Hunting, Incident Investigation, Adversary Infrastructure Analysis, Detection Engineering, IR Lifecycle, MITRE ATT\&CK, TTPs, IOC/IOA Analysis, Playbook Development, SOAR
    \item \textbf{Detection \& Platform Engineering}: CrowdStrike LogScale, Microsoft Sentinel (KQL), Detection Rule Development, Security Telemetry Engineering, Automation Workflows
    \item \textbf{Threat Intelligence \& OSINT}: MISP, AbuseIPDB, Abuse.ch, Shodan, Maltiverse, Lumu, SpiderFoot, Maltego, Recon-ng, IOC Analysis, IOA Analysis
    \item \textbf{Vulnerability Management}: Nessus, Greenbone, Cavelo, CVSS, Vulnerability Assessment, Remediation Tracking, Risk Assessment
    \item \textbf{Digital Forensics}: Autopsy, FTK Imager, Sleuth Kit, Wireshark, HxD Hex Editor, Jump List Analysis, Prefetch Analysis, USB Forensic Tracker, HashMyFiles
    \item \textbf{Security Workflow \& Automation}: PowerShell, Python, Bash Scripting, n8n, CrowdStrike Fusion, SOAR, Playbook Development
    \item \textbf{Cloud \& Identity Management}: Microsoft Azure, Microsoft Intune, Active Directory, Google Cloud Platform (GCP), AWS
    \item \textbf{Frameworks \& Methodology}: NIST CSF, MITRE ATT\&CK, Zero Trust, Defense in Depth, Incident Response Framework, Kill Chain
    \item \textbf{Networking}: TCP/IP, OSI Model, VLANs, Network Traffic Analysis, Cisco Packet Tracer
    \item \textbf{Virtualization \& Labs}: VMware, VirtualBox, Proxmox Virtual Environment, FLARE VM, Docker
    \item \textbf{Operating Systems}: Windows, Windows Server, Linux, Ubuntu, Kali Linux, Parrot OS, macOS
    \item \textbf{Languages}: English (Fluent), French (Fluent -- Professional Proficiency)
\end{itemize}

%-----PROJECTS-----------------------------------------------------------------
\section{Projects}
  \CVSubHeadingListStart

    \CVSubheading
      {{Cyber Risk Assessment \& Management} $|$ \emph{\small{NIST CSF, MITRE ATT\&CK}}}{Spring 2023}
      {John Jay College of Criminal Justice}{}
      \CVItemListStart
        \CVItem{Developed a comprehensive Information Security and Privacy Program incorporating Zero Trust, Defense in Depth, and Agile Security frameworks.}
        \CVItem{Applied cyber risk mitigation strategies and threat modeling techniques; built a risk mitigation plan addressing high-risk threats to support long-term cyber maturity.}
      \CVItemListEnd

    \CVSubheading
      {{Azure Sentinel SIEM -- Live Cyber Attack Map} $|$ \emph{\small{PowerShell, KQL}}}{Fall 2022}
      {John Jay College of Criminal Justice}{}
      \CVItemListStart
        \CVItem{Used a custom PowerShell script to extract metadata from Windows Event Viewer and forward it to a third-party geolocation API.}
        \CVItem{Configured Microsoft Sentinel workbook to display global RDP brute-force attack data on a world map, visualizing attack origin and magnitude in real time.}
      \CVItemListEnd

    \CVSubheading
      {{Digital Forensic Investigation} $|$ \emph{\small{Autopsy, FTK Imager, Prefetch, Jump List, HashMyFiles}}}{Spring 2022}
      {John Jay College of Criminal Justice}{}
      \CVItemListStart
        \CVItem{Served as Forensic Investigator, collecting and preserving digital evidence from forensic images across multiple case scenarios involving data theft and unauthorized intrusion.}
        \CVItem{Maintained Chain of Custody documentation and produced comprehensive investigative reports for each case.}
      \CVItemListEnd

    \CVSubheading
      {{Autonomous Air Quality Monitoring Robot} $|$ \emph{\small{C++, C, Raspberry Pi}}}{Fall 2021}
      {John Jay College of Criminal Justice}{}
      \CVItemListStart
        \CVItem{Developed embedded C/C++ software for Raspberry Pi-based autonomous indoor navigation with integrated environmental sensors and data logging for air quality analysis.}
      \CVItemListEnd

  \CVSubHeadingListEnd

\end{document}
